Visual Diagnostics for Constrained Optimisation with Application to Guided Tours

### 2021-03-17 paper/zhang-cook-laa-langrene-menendez.Rmd
changes on optim methods done

Random search [in practice, non-convex, non-smooth]. The original (pure) random search, Brooks, randomly evaluate points in the space regardless of the current position. Although gaurantee global convergence, as the dimensional increases, blindly sample points in the entire space would cost a long time for convergence to occur [spall, 6]. Various algorithms improve on the pure random search by either concentrating on a narrower sampling space or a different updating machanism. Creeping random search, [R.C White], is such a variation where a candidate point is generated within a neighbourhood of the current point and the current point is only updated if the candidate point makes an improvment on the function value. [no convergence guarantee]. A different random search algorithm, simulated annealing, takes a different updating procedure than creeping random search. Rather than only updating the current point when an improvement is made, simulated annealing uses a Metropolis acceptance criterion, where nonimproving candidates can still have a chance to be accepted. The convergence of simulated annealing algorithms has been widely researched [reference, reference, reference] and a global convergence is guaranteed [under what condition].

>>>>

Random search mehtods [@zabinsky2013stochastic] contain a random sampling component in its algorithm and has shown its ability to optimise non-convex and non-smooth functions. The initial random search algorithm, pure random search [@Brooks1958-zk], draws candidate points from the entire space without using any information of the current position and updates the current position when an improvement on the objective function is made. As the dimension of the space becomes larger, sampling from the entire space would indicate a long time for convergence to occur despite a guaranteed global convergence [@spall2005introduction]. Various algorithms have then been developed to improve pure random search by either concentrating on a narrower sampling space or using a different updating machanism. Creeping random search [@White1971-ci] is such a variation where a candidate point is generated within a neighbourhood of the current point. This gives creeping random search an advantage of being fast to compute, however, global convergence is not longer guaranteed. On the other hand, simulated annealing [@kirkpatrick1983optimization; @bertsimas1993simulated], takes a different updating machanism from the pure random search. Rather than only updating the current point when an improvement is made, simulated annealing uses a Metropolis acceptance criterion, where nonimproving candidates can still have a chance to be accepted. The convergence of simulated annealing algorithms has been widely researched [@mitra1986convergence; @belisle1992convergence; @granville1994simulated] and the global optimum can be attained under mild conditions.

### 2021-03-17 paper/zhang-cook-laa-langrene-menendez.tex
changes on optim methods done

Random search {[}in practice, non-convex, non-smooth{]}. The original
(pure) random search, Brooks, randomly evaluate points in the space
regardless of the current position. Although gaurantee global
convergence, as the dimensional increases, blindly sample points in the
entire space would cost a long time for convergence to occur {[}spall,
6{]}. Various algorithms improve on the pure random search by either
concentrating on a narrower sampling space or a different updating
machanism. Creeping random search, {[}R.C White{]}, is such a variation
where a candidate point is generated within a neighbourhood of the
current point and the current point is only updated if the candidate
point makes an improvment on the function value. {[}no convergence
guarantee{]}. A different random search algorithm, simulated annealing,
takes a different updating procedure than creeping random search. Rather
than only updating the current point when an improvement is made,
simulated annealing uses a Metropolis acceptance criterion, where
nonimproving candidates can still have a chance to be accepted. The
convergence of simulated annealing algorithms has been widely researched
{[}reference, reference, reference{]} and a global convergence is
guaranteed {[}under what condition{]}.

>>>>

Random search mehtods \citep{zabinsky2013stochastic} contain a random
sampling component in its algorithm and has shown its ability to
optimise non-convex and non-smooth functions. The initial random search
algorithm, pure random search \citep{Brooks1958-zk}, draws candidate
points from the entire space without using any information of the
current position and updates the current position when an improvement on
the objective function is made. As the dimension of the space becomes
larger, sampling from the entire space would indicate a long time for
convergence to occur despite a guaranteed global convergence
\citep{spall2005introduction}. Various algorithms have then been
developed to improve pure random search by either concentrating on a
narrower sampling space or using a different updating machanism.
Creeping random search \citep{White1971-ci} is such a variation where a
candidate point is generated within a neighbourhood of the current
point. This gives creeping random search an advantage of being fast to
compute, however, global convergence is not longer guaranteed. On the
other hand, simulated annealing
\citep{kirkpatrick1983optimization, bertsimas1993simulated}, takes a
different updating machanism from the pure random search. Rather than
only updating the current point when an improvement is made, simulated
annealing uses a Metropolis acceptance criterion, where nonimproving
candidates can still have a chance to be accepted. The convergence of
simulated annealing algorithms has been widely researched
\citep{mitra1986convergence, belisle1992convergence, granville1994simulated}
and the global optimum can be attained under mild conditions.
